Four Models for Severe Weather Deaths

### 2017-05-10 paper.Rnw
Fixed Screwy ZIP DIC Code

\begin{table}
\centering
\caption{The following table shows the resulting DIC and WAIC for each of the four models on both the tornado data and the flash flood data. In the case of the zero inflated negative binomial model, WAIC was too computationally expensive, so it was not calculated.}
\label{t:evalresults}
\begin{tabular}{lcccc}
\toprule
&\multicolumn{2}{c}{Flash Flood}&\multicolumn{2}{c}{Tornado}\\
\cmidrule(r){2-3}\cmidrule(l){4-5}
Model & DIC &WAIC & DIC &WAIC\\
\midrule
Poisson & P FLOOD DIC& P FLOOD WAIC &P TORNADO DIC&P TORNADO WAIC\\
Negative Binomial & NB FLOOD DIC& NB FLOOD WAIC &NB TORNADO DIC&NB TORNADO WAIC\\
ZIP & 3845.915& ZIP FLOOD WAIC &4759.998 &ZIP TORNADO WAIC\\
ZINB & \Sexpr{flood.dic.zinb}& -- &\Sexpr{tornado.dic.zinb}&--\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption{The following table shows the resulting DIC and WAIC for each of the four models on both the tornado data and the flash flood data. In the case of the zero inflated negative binomial model, WAIC was too computationally expensive, so it was not calculated.}
\label{t:evalresults}
\begin{tabular}{lcccc}
\toprule
&\multicolumn{2}{c}{Flash Flood}&\multicolumn{2}{c}{Tornado}\\
\cmidrule(r){2-3}\cmidrule(l){4-5}
Model & DIC &WAIC & DIC &WAIC\\
\midrule
Poisson & P FLOOD DIC& P FLOOD WAIC &P TORNADO DIC&P TORNADO WAIC\\
Negative Binomial & NB FLOOD DIC& NB FLOOD WAIC &NB TORNADO DIC&NB TORNADO WAIC\\
ZIP & 10454.860& ZIP FLOOD WAIC &8727.647 &ZIP TORNADO WAIC\\
ZINB & \Sexpr{flood.dic.zinb}& -- &\Sexpr{tornado.dic.zinb}&--\\
\bottomrule
\end{tabular}
\end{table}
